A Reduced Representation for Computational Fabrication

### 2013-01-11 paper.tex
abstract

\begin{abstract}
Computational fabrication problems are often concerned with optimal material assignment.

They attempt to compute a spatially varying material distribution that yields specified real-world behavior.

In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms.

We illustrate the utility of our framework by showing implemented fabrication algorithms as well as their manufactured results.

\end{abstract}

>>>>

\begin{abstract}
Digital fabrication allows to virtually design objects and then translate them to the corresponding physical equivalents.
With the increasing popularity of multi-material 3D printing, these objects can be composed from multiple materials that have different properties.
A key computational problem is how to compute a spatially varying material distribution that yields specified real-world behavior of the object.
During the last few years a number of instances of this problem have been examined that tackle different aspects of object behavior, e.g.,  appearance or elastic deformation.
In this paper, we propose an abstraction mechanism that simplifies the design, development, and implementation of these processes.
Our solution relies on two data structures: a graph-based reducer network that efficiently parameterizes the space of material assignments and a tuner network that describes the optimization process to achieve desired material assignment. A corresponding API provides a natural way of specifying user-defined translation processes and the desired object.  
We illustrate the utility of our framework by showing implemented fabrication algorithms as well as the corresponding manufactured results.
\end{abstract}
